Synthesizing Symmetric Lenses

### 2018-07-04 papers/SymmetricLenses/main.tex
Finished proof of Theorem 4

where
$$\ConcatSequenceOf{[\String_0\SeqSep\Atom_1\SeqSep\ldots\SeqSep\Atom_n\SeqSep\String_n]}{[\StringAlt_0\SeqSep\AtomAlt_1\SeqSep\ldots\SeqSep\AtomAlt_m\SeqSep\StringAlt_m]}=
  [\String_0\SeqSep\Atom_1\SeqSep\ldots\SeqSep\Atom_n\SeqSep\String_n\Concat\StringAlt_0\SeqSep\AtomAlt_1\SeqSep\ldots\SeqSep\AtomAlt_m\SeqSep\StringAlt_m]$$
Hence
$$P_{\langle (SQ_1, p_1) \; | \; \ldots \; | \;(SQ_n,p_n)\rangle \odot \langle (TQ_1, q_1) \; | \; \ldots \; | \;(TQ_m,q_m)\rangle}(s) = \sum_{i=1}^n \sum_{j=1}^m(p_i * q_j) * P_{SQ_i \odot_{SQ} TQ_j}(s)$$
Since $P_{[s_0 \cdot A_1 \cdot \ldots \cdot A_n \cdot s_n]}(s) = \sum_{s_0 \cdot s'_1 \cdot \ldots \cdot s'_n \cdot s_n = s} \prod_{i=1}^n P_{A_i}(s'i)$, then
\begin{align*}
P_{[s_0 \cdot A_1 \cdot \ldots \cdot A_n \cdot s_n] \odot_{SQ} [t_0 \cdot B_1 \cdot \ldots \cdot B_m \cdot t_m]}(s) &= \sum_{s_0 \cdot s'_1 \cdot \ldots \cdot s'_n \cdot s_n \cdot t_0 \cdot t'_1 \cdot \ldots t'_m \cdot t_m =s } \prod_{i=1}^n P_{A_i}(s'_i) \prod_{j=1}^m P_{B_j}(t'_j)\\
&= \sum_{a \cdot b = s} \sum_{s_0 \cdot s'_1 \cdot \ldots \cdot s'_n \cdot s_n = a} \sum_{t_0 \cdot t'_1 \cdot \ldots \cdot t'_m \cdot t_m = b} \prod_{i=1}^n P_{A_i}(s'_i) \prod_{j=1}^m P_{B_j}(t'_j)\\
& \sum_{a \cdot b = s} \left(\sum_{s_0 \cdot s'_1 \cdot \ldots \cdot s'_n \cdot s_n = a} \prod_{i=1}^n P_{A_i}(s'_i)\right) \left(\sum_{t_0 \cdot t'_1 \cdot \ldots \cdot t'_m \cdot t_m = b} \prod_{j=1}^m P_{B_j}(t'_j)\right)\\
&= \sum_{a \cdot b = s}P_{[s_0 \cdot A_1 \cdot \ldots \cdot A_n \cdot s_n]}(a) * P_{[t_0 \cdot B_1 \cdot \ldots \cdot B_m \cdot t_m]}(b)
\end{align*}
In other words, $P_{SQ \odot_{SQ} TQ}(s) = \sum_{a \cdot b = s}P_{SQ}(a) * P_{TQ}(b)$. Hence, 
\begin{align*}
P_{S_1 \cdot S_2}(s) &= \sum_{i=1}^n \sum_{j=1}^m (p_i * q_j)\sum_{s_1 \cdot s_2 = s} (P_{SQ_i}(s_1) *  P_{TQ_j}(s_2))\\
&= \sum_{i=1}^n \sum_{j=1}^m (p_i * q_j)\sum_{s_1 \cdot s_2 = s} P_{SQ_i \odot_{SQ} TQ_j}(s)\\
&= P_{\langle (SQ_1, p_1) \; | \; \ldots \; | \;(SQ_n,p_n)\rangle \odot \langle (TQ_1, q_1) \; | \; \ldots \; | \;(TQ_m,q_m)\rangle}(s)\\
&= P_{(\Downarrow S_1) \odot (\Downarrow S_2)}(s)
\end{align*}
which is what we wanted to show.
\item
\end{enumerate}
\end{proof}
\end{document}

>>>>

where
$$\ConcatSequenceOf{[\String_0\SeqSep\Atom_1\SeqSep\ldots\SeqSep\Atom_n\SeqSep\String_n]}{[\StringAlt_0\SeqSep\AtomAlt_1\SeqSep\ldots\SeqSep\AtomAlt_m\SeqSep\StringAlt_m]}=
  [\String_0\SeqSep\Atom_1\SeqSep\ldots\SeqSep\Atom_n\SeqSep\String_n\Concat\StringAlt_0\SeqSep\AtomAlt_1\SeqSep\ldots\SeqSep\AtomAlt_m\SeqSep\StringAlt_m]$$
Hence
$$P_{\langle (SQ_1, p_1) \; | \; \ldots \; | \;(SQ_n,p_n)\rangle \odot \langle (TQ_1, q_1) \; | \; \ldots \; | \;(TQ_m,q_m)\rangle}(s) = \sum_{i=1}^n \sum_{j=1}^m(p_i * q_j) * P_{SQ_i \odot_{SQ} TQ_j}(s)$$
Since $P_{[s_0 \cdot A_1 \cdot \ldots \cdot A_n \cdot s_n]}(s) = \sum_{s_0 \cdot s'_1 \cdot \ldots \cdot s'_n \cdot s_n = s} \prod_{i=1}^n P_{A_i}(s'i)$, then
\begin{align*}
P_{[s_0 \cdot A_1 \cdot \ldots \cdot A_n \cdot s_n] \odot_{SQ} [t_0 \cdot B_1 \cdot \ldots \cdot B_m \cdot t_m]}(s) &= \sum_{s_0 \cdot s'_1 \cdot \ldots \cdot s'_n \cdot s_n \cdot t_0 \cdot t'_1 \cdot \ldots t'_m \cdot t_m =s } \prod_{i=1}^n P_{A_i}(s'_i) \prod_{j=1}^m P_{B_j}(t'_j)\\
&= \sum_{a \cdot b = s} \sum_{s_0 \cdot s'_1 \cdot \ldots \cdot s'_n \cdot s_n = a} \sum_{t_0 \cdot t'_1 \cdot \ldots \cdot t'_m \cdot t_m = b} \prod_{i=1}^n P_{A_i}(s'_i) \prod_{j=1}^m P_{B_j}(t'_j)\\
& \sum_{a \cdot b = s} \left(\sum_{s_0 \cdot s'_1 \cdot \ldots \cdot s'_n \cdot s_n = a} \prod_{i=1}^n P_{A_i}(s'_i)\right) \left(\sum_{t_0 \cdot t'_1 \cdot \ldots \cdot t'_m \cdot t_m = b} \prod_{j=1}^m P_{B_j}(t'_j)\right)\\
&= \sum_{a \cdot b = s}P_{[s_0 \cdot A_1 \cdot \ldots \cdot A_n \cdot s_n]}(a) * P_{[t_0 \cdot B_1 \cdot \ldots \cdot B_m \cdot t_m]}(b)
\end{align*}
In other words, $P_{SQ \odot_{SQ} TQ}(s) = \sum_{a \cdot b = s}P_{SQ}(a) * P_{TQ}(b)$. Hence, 
\begin{align*}
P_{S_1 \cdot S_2}(s) &= \sum_{i=1}^n \sum_{j=1}^m (p_i * q_j)\sum_{s_1 \cdot s_2 = s} (P_{SQ_i}(s_1) *  P_{TQ_j}(s_2))\\
&= \sum_{i=1}^n \sum_{j=1}^m (p_i * q_j)\sum_{s_1 \cdot s_2 = s} P_{SQ_i \odot_{SQ} TQ_j}(s)\\
&= P_{\langle (SQ_1, p_1) \; | \; \ldots \; | \;(SQ_n,p_n)\rangle \odot \langle (TQ_1, q_1) \; | \; \ldots \; | \;(TQ_m,q_m)\rangle}(s)\\
&= P_{(\Downarrow S_1) \odot (\Downarrow S_2)}(s)
\end{align*}
which is what we wanted to show.
\item
$(S = S_1 \; |_p \; S_2)$

By definition $\Downarrow (S_1 \; |_p \; S_2) = (\Downarrow S_1) \oplus_p (\Downarrow S_2)$. By the induction hypothesis $P_{S_1} = P_{\Downarrow S_1}$ and $P_{S_2} = P_{\Downarrow S_2}$. Assume that $\Downarrow S_1 = \langle (SQ_1,p_1) \; | \; \ldots \; | \; (SQ_m, p_n)\rangle$ and $\Downarrow S_2 = \langle (TQ_1,q_1) \; | \; \ldots \; | \; (TQ_n, q_m) \rangle$. By definition,

  $\OrDNFOf{\DNFOf{(\Sequence_1,\Probability_1)\DNFSep\ldots\DNFSep(\Sequence_n,\Probability_n)}}{\DNFOf{(\SequenceAlt_1,\ProbabilityAlt_1)\DNFSep\ldots\DNFSep(\SequenceAlt_m,\ProbabilityAlt_m)}}{\Probability} =$\\
  $\DNFOf{(\Sequence_1,\Probability_1*\Probability)\DNFSep\ldots\DNFSep(\Sequence_n,\Probability_n*\Probability)\DNFSep(\SequenceAlt_1,\ProbabilityAlt_1*(1-\Probability))\DNFSep\ldots\DNFSep(\SequenceAlt_m,\ProbabilityAlt_m*(1-\Probability))}$
  hence
  \begin{align*}
  P_{(\Downarrow S_1) \; |_p \; (\Downarrow S_2)}(s) &= P_{\langle (SQ_1,p_1) \; | \; \ldots \; | \; (SQ_n, p_n)\rangle \oplus_p \langle (TQ1, q_1) \; | \; \ldots \; | \; (TQ_m, q_m)\rangle}(s) \\
  &= P_{\langle (SQ_1,p_1) \; | \; \ldots \; | \; (SQ_n, p_n) \; | \; (TQ1, q_1) \; | \; \ldots \; | \; (TQ_m, q_m)\rangle}(s)\\
  &= \sum_{i=1}^m (p * p_i) P_{SQ_i}(s) + \sum_{j=1}^m ((1-p) * q_j) P_{TQ_j}(s)\\
  &= p * \sum_{i=1}^m p_i P_{SQ_i}(s) + (1-p)* \sum_{j=1}^m q_j * P_{TQ_j}(s)\\
&= p * P_{\langle (SQ_1,p_1) \; | \; \ldots \; | \; (SQ_n, p_n)\rangle}(s) + (1-p) * P_{\langle (TQ1, q_1) \; | \; \ldots \; | \; (TQ_m, q_m)\rangle}(s)\\
&= p * P_{\Downarrow S_1}(s) + (1-p) * P_{\Downarrow S_2}(s) 
  \end{align*}

  Since $P_{S_1} = P_{\Downarrow S_1}$ and $P_{S_1} = P_{\Downarrow S_1}$, then 
  \begin{align*}
  P_{S_1}(s) &= \sum_{i=1}^n p_i * P_{SQ_i}(s)\\
  P_{S_2}(s) &= \sum_{j=1}^m q_m * P_{TQ_j}(s)
  \end{align*}
  hence
  \begin{align*}
  P_{S_1 \; |_p \; S_2}(s) &= p * (P_{S_1}(s)) + (1-p) * (P_{S_2}(s))\\
  &= p \left(\sum_{i=1}^n p_i * P_{SQ_i}(s)\right) + (1-p)\left(\sum_{j=1}^m q_m * P_{TQ_j}(s)\right)\\
  &= p * P_{\Downarrow S_1}(s) + (1-p) * P_{\Downarrow S_2}(s)\\
  &= P_{(\Downarrow S_1) \; |_p \; (\Downarrow S_2)}(s)
  \end{align*}
  which is what we wanted to show. This completes the proof.
\end{enumerate}
\end{proof}
\end{document}
